### 2015-11-24 Manuscript/BiologyLetters/CoverLetter.tex
list of reviewers
Cover letter update

% PLoS Biology cover letter:
% Upload a cover letter as a separate file in the online system. The length limit is 600 words.

% The cover letter should address the following questions:

%     What is the scientific question you are addressing?
% "investigate whether mammal diversity was directly affected by the K-Pg mass extinction."
%     What is the key finding that answers this question?
% "We find no evidence for a direct effect of the K-Pg extinction event on mammalian diversification."
%     What is the nature of the evidence you provide in support of your conclusion?
% The time slicing method and using both data?
%     What are the three most recently published articles that are relevant to this question?
% Slater 2013 Methods Ecol. Evol.; Beck \& Lee 2014 Proc. Roy. Soc. B Close et al. 2015 Current Biol. (Or maybe put O'Leary?)
%     What significance do your results have for the field?
% Proposing new methods to investigate disparity-through-time in a continuous way + using both living and fossil taxa
%     What significance do your results have for the broader community (of biologists and/or the public)?
% Text book example.
%     What other novel findings do you present?
% Effect of using both data sources
%     Is there additional information that we should take into account?
% Graeme's story?

% TG: Ok, nothing too complex here, just some reformatting maybe. Everything is clearly stated in the Nature Comm version but not in their order. Maybe do a bullet point alternative version?

@@

Combining fossils into phylogenies is cool
We can use TEM method along side with tip-dating
However, to eficiently do it, it is important to have enough data for living species for allowing the fossil ones to branch correctly (Guillerme and Cooper 2016, Molecular Phylogenetics and Evolution)

In this research article, entitled ``Investigating the effects of the Cretaceous-Paleogene mass extinction on mammalian morphological diversity using a new methodological approach'', we use both data from living and fossil species through Total Evidence tip-dated phylogenies along with a novel continuous time-slicing method to investigate whether mammalian morphological diversity was directly affected by the K-Pg event.

We look forward to hearing from you,

@@

% Editors
% Dean Adams?
% Matt Friedman?
% Daniel Rabosky?
% Liam Revell?

% Suggested reviewers:
% Graeme Lloyd
% Robin Beck
% Robert Close
% Mike Benton or Steve Brusatte or Richard Butler (they're cited a lot)
% Any other ideas?

% Yep all good.
% BUT if you want to suggest Graeme you need to add the postscript I added above. You may need to alter the reference.

>>>>

@@

%TG: That's word for word the TEM paper cover letter
In recent years there has been growing interest in building phylogenies that contain both living and fossil taxa (e.g. Quental and Marshall 2006 TREE; Fritz et al. 2013 TREE; Heath et al. 2014 PNAS).
Such phylogenies could revolutionize the way we think about macroevolutionary patterns and processes, and provide a more complete understanding of trends in biodiversity through time.

One method, the Total Evidence method, allows us to use molecular and morphological data to build phylogenies with both living and fossil species as tips (Ronquist et al. 2012 Syst Biol).
%TG: it changes from here:
This method is extremely promising because it allows us to use all the available data. However, to efficiently apply this method, it is crucial to have enough morphological data for living species for allowing the fossil ones to branch correctly into the phylogeny (Guillerme and Cooper 2016, Molecular Phylogenetics and Evolution).

Our research article, entitled ``Assessment of cladistic data availability for living mammals'', is to our knowledge, the first to thoroughly assess the availability of cladistic (morphological) data in living mammals.
Additionally, we test whether the available data in each mammalian order is randomly distributed or clustered towards certain clades to investigate whether the placement of fossil taxa within these order would have respectively non \textit{a priori} bias or would be bias towards the clades with the most data.

Our results show that, unfortunately 22 of 28 mammalian orders have less than 25\% species with available morphological data.
Fortunately, however, most of this available data was randomly distributed across each mammalian order expect for 6 for which the data was biased towards certain clades.
We hope that our work will encourage cladisticians %TG: or is that how there are called?
to sample more data for living species and thus serving as a stepping stone for improving combining living and fossil taxa in the same phylogenies.

We look forward to hearing from you soon,

@@

% Editors
% Paul Barrett? Or do they have one assigned for the issue already

% Suggested reviewers:
% Fred Ronquist
% Alex Pyron (since he already reviewed the other one)
% Phil Donoghue (but conflict of interest?)
% O'Leary (even if you know I hate the Science paper, we mention morphoBank in a positive light)
